---
title: "Linear Regression TC"
author: "Adrian Bumbas"
date: "23 October 2015"
output: html_document
---
###My solution fo the [Fun Series October - Learning Data Science - Linear Regression](https://www.topcoder.com/challenge-details/30051596/?type=develop) challenge


Let's first read the CSV file into a data frame:

```{r}
df <- read.table("input/pts.csv", header=T, sep=",", quote="")

```

There are 3 columns:
```{r}
names(df)
```
..and 20 sets:
```{r}
str(factor(df$set))
```
Let's build the dataframe where we will store the result:
```{r}
result<-data.frame()
```

Next we are going to loop trough all the dataset and calculate a linear model using 'lm()'
```{r}
for(x in 1:20){
  #for each set
  set <- df[df$set == x,]
  
  #calculate linear model
  lm_set<-lm(x~y,data = set)
  
  #add the coefficients and the datatset number to the result
  result<-rbind(result,data.frame(x,coef(lm_set)[2],coef(lm_set)[1]))
 
}
```

Finally write the data frame to a CSV file
```{r}
write.table(result, file = "result.csv",row.names=FALSE, na="",col.names=FALSE, sep=",")
```

Things to do:

* Check RMSE
* Check R squared
* Optimize the model

